State of the Practice of Lattice Boltzmann Method Software Development

### 2021-06-02 StateOfPractice/Peter-Notes/Report/Report.tex
1st edits to methodology section of LBM Report

In this project we set out to answer the research questions found in Section \ref{researchquestions} for the Lattice Boltzmann scientific computing software domain. The process involved systematically measuring and analyzing members of this software family along the quality attributes found in Section \ref{softwarequalities}. This included gathering quantitative and qualitative measurements. A goal of the project was to also produce a hierarchical quality assessment for LBM software.

We collected quantitative data using the measures found in the measurement template of Section \ref{measurementtemplate}. Some of this was empirical software engineering related data, such as the number of files, number of lines of code, percentage of issues that are closed. Most was gathered by manually observing the software, it's source code, and it's artifacts, while some was gathered using the tools listed in Section \ref{tools}.

We also collected qualitative data by interviewing the software package developers and asking them the questions found in Section \ref{interviewquestions}. Furthermore, we solicited the assistance of domain experts to better access each software package by leveraging their experience to access the functional and non-functional domain software requirements.

This section begins with the steps of the overall process we used to select, measure and compare LBM software. This is followed by quality definitions and how they were applied in our project. The rest of the section provides an overview of how candidate software packages were selected and filtered, the empirical measurements and software tools, and the analytic hierarchy process (AHP).

>>>>

In this project we set out to answer the research questions found in Section \ref{researchquestions} for the LBM SCS domain. The process involved systematically measuring and analyzing members of this software family along the quality attributes found in Section \ref{softwarequalities}. This included gathering quantitative and qualitative measurements. A goal of the project was to produce a hierarchical quality assessment for LBM software packages.

We collected quantitative data using the measures found in the measurement template of Section \ref{measurementtemplate}. Some of this was empirical software engineering related data, such as the number of files, number of lines of code, percentage of issues that are closed. Most of the data was gathered by manually observing the software, its source code, and its artifacts, while some was gathered using the tools listed in Section \ref{tools}.

We also collected qualitative data by interviewing the software package developers and asking them the questions found in Section \ref{interviewquestions}. Furthermore, we solicited the assistance of domain experts to better assess each software package by leveraging their experience to assess the functional and non-functional requirements for the software domain.

This section begins by describing the steps of the overall process we used to select, measure and compare LBM software. This is followed by quality definitions and how these qualities were assessed in our project. The rest of the section provides an overview of how candidate software packages were selected and filtered, the empirical measurements and software tools that were used, and the analytic hierarchy process (AHP).
